A generalized definition of multidimensional item response theory parameters

### 2024-04-29 output/paper_draft/paper_M2PLM_parameters.Rmd
Implements changes approved in Google Docs
Implements changes approved in MLV's review on 2024-04-28 in section "Test space and latent space"

Let $`r TEST_SPACE`$ be the vector space made up by
the set of $`r DISCR_VECTOR`$ vectors,
with the sum and product by a scalar operation as in $`r REAL_N_SPACE`$.
We want @reckase_difficulty_1985's definition of
the multidimensional parameters in rectangular coordinates to be
a particular case of our more general definition;
we can thus consider an orthonormal basis $`r TEST_SPACE_STD_BASIS`$
in $`r TEST_SPACE`$ such that $`r DISCR_STD_COORDS_ALT_EQ`$
corresponds in the model to $`r TRAIT_ORTH_COORDS`$.
Since the response probability to the `r MODEL_ACRONYM`,
given by \@ref(eq:M2PL-formulation), must be invariant with respect to
the change of basis expressed in \@ref(eq:change-basis),
Therefore, we find a basis $`r TEST_SPACE_BASIS`$ in $`r TEST_SPACE`$
defined by

@@

with $`r TRANSFORM_MATRIX_TRANSP_INV`$ a change of basis matrix.
Note that, as $`r TEST_SPACE_STD_BASIS`$ is orthonormal,
$`r TRANSFORM_MATRIX_TRANSP_INV`$ determines $`r TEST_SPACE_BASIS`$.

>>>>

Let $`r TEST_SPACE`$ be the vector space made up by
the set of $`r DISCR_VECTOR`$ vectors,
with the operations sum and product by a scalar as in $`r REAL_N_SPACE`$.
We want @reckase_difficulty_1985's definition of
the multidimensional parameters in rectangular coordinates to be
a particular case of our more general definition;
we can thus consider an orthonormal basis $`r TEST_SPACE_STD_BASIS`$
in $`r TEST_SPACE`$ such that $`r DISCR_STD_COORDS_ALT_EQ`$
corresponds in the model to $`r TRAIT_ORTH_COORDS`$.
Since the response probability to the `r MODEL_ACRONYM`,
given by Equation \@ref(eq:M2PL-formulation), must be invariant with respect to
the change of basis expressed in Equation \@ref(eq:change-basis),
$`r INVARIANCE_EQ`$.
Therefore, we find a basis $`r TEST_SPACE_BASIS_EQ`$ in $`r TEST_SPACE`$
defined by

@@

with $`r TRANSFORM_MATRIX_TRANSP_INV`$ a change of basis matrix.
Note that $`r TRANSFORM_MATRIX_TRANSP_INV`$ determines $`r TEST_SPACE_BASIS`$.
